Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-07 paper.tex
Introduce variable for number of operating reactors to simplify discussion.

    \item Reactor capacity is deployed and retired in single reactor units
        (e.g. 1 GWe LWRs).

@@

        \begin{equation}
            D =
            \frac{B}{L} \cdot N_{r} \cdot \frac{C_{inv}}{C_{cap}}
            \label{eqn:fleet-discharge}
        \end{equation}

        $D$ is the discharge rate (kg per time step), $B$ is the batch size
        (kg) for a single reactor's batch, $L$ is the cycle length (including
        refueling time) in time steps, $N_{r}$ is the number of reactors in
        the fleet, $C_{inv}$ is the total amount of fuel in all reactor cores
        (kg), and $C_{cap}$ is the total fuel capacity for all reactor cores
        (kg).  The last fractional term accounts for lower fuel burning rates
        due to unfueled reactors.

@@

    \item Generated power is computed similarly to core discharge rates by
        multiplying the total fleet power capacity by the same last fractional
        term of Equation \ref{eqn:fleet-discharge} to account for unfueled
        capacity in the fleet.

>>>>

    \item Reactor capacity is deployed and retired in increments of single
      reactor units, each with capable of producing power $P_r$ (e.g. 1 GWe
      LWRs).  $N_{r}$ reactors are deployed at any time capable of producing
      $P_r \cdot N_r$ power.

    \item In the event of fuel shortages, the number of reactors that can
      operate is modeled as

      \begin{equation}
        N_{o} = N_{r} \cdot \frac{C_{inv}}{C_{cap}},
        \label{eqn:operating-reactors}
      \end{equation}

       where $C_{inv}$ is the total amount of fuel in all reactor cores (kg),
       and $C_{cap}$ is the total fuel capacity for all reactor cores (kg).

@@

        \begin{equation}
            D =
            \frac{B}{L} \cdot N_{o} =  \frac{B}{L} \cdot N_{r}\cdot \frac{C_{inv}}{C_{cap}}
            \label{eqn:fleet-discharge}
        \end{equation}

        $D$ is the discharge rate (kg per time step), $B$ is the batch size
        (kg) for a single reactor's batch, $L$ is the cycle length (including
        refueling time) in time steps.  In the event of fuel shortages, the
        discharge rate is reduced because some reactors are not operating.

@@

    \item Generated power at any timestep, $P_G$, is based on the number of
      operating reactors:

      \begin{equation}
        P_{G} = P_r \cdot N_o = P_r \cdot N_r \cdot \frac{C_{inv}}{C_{cap}}
      \end{equation}
